---
title: "HW3"
author: "Mehmet Akif Taşcıoğlu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(ggplot2)
library(rpart)
library(dtw)
library(wavelets)
library(TunePareto)
library(data.table)
library(rattle)
library(zoo)
library(repr)
library(TSrepr)
library(Rcpp)
library(genlasso)
```


# Comparison of NN classifiers with alternative representations
In this assignment, 5 datasets are selected from http://www.timeseriesclassification.com webpage.The aim of this task is to compare alternative distance measures for classification.


```{r}
nn_classify_cv=function(dist_matrix,train_class,test_indices,k=1){
    
    test_distances_to_train=dist_matrix[test_indices,]
    test_distances_to_train=test_distances_to_train[,-test_indices]
    train_class=train_class[-test_indices]
    ordered_indices=apply(test_distances_to_train,1,order)
    if(k==1){
        nearest_class=as.numeric(trainclass[as.numeric(ordered_indices[1,])])
        nearest_class=data.table(id=test_indices,nearest_class)
    } else {
        nearest_class=apply(ordered_indices[1:k,],2,function(x) {trainclass[x]})
        nearest_class=data.table(id=test_indices,t(nearest_class))
    }
    long_nn_class=melt(nearest_class,'id')
    class_counts=long_nn_class[,.N,list(id,value)]
    class_counts[,predicted_prob:=N/k]
    wide_class_prob_predictions=dcast(class_counts,id~value,value.var='predicted_prob')
    wide_class_prob_predictions[is.na(wide_class_prob_predictions)]=0
    class_predictions=class_counts[,list(predicted=value[which.max(N)]),by=list(id)]
    return(list(prediction=class_predictions,prob_estimates=wide_class_prob_predictions))
    
}
```


## Dataset 1: Powercons


```{r}
setwd("C:/Users/User/Desktop/ie48b/hw3")
powercons_train_data <- fread("PowerCons_TRAIN.txt")
powercons_test_data <- fread("PowerCons_TEST.txt")

setnames(powercons_train_data,"V1","class")
powercons_train_data=powercons_train_data[order(class)]
powercons_train_data[,class:=as.character(class)]
powercons_train_data[,id:=1:.N]
powercons_train_data_long=melt(powercons_train_data,id.vars=c('id','class'))
powercons_train_data_long[,time:=as.numeric(gsub("\\D", "", variable))-1]
powercons_train_data_long=powercons_train_data_long[,list(id,class,time,value)]
powercons_train_data_long=powercons_train_data_long[order(id,time)]
head(powercons_train_data_long)
```



```{r}

plot(x = powercons_train_data_long[id == 1 & class == 1]$time,y = powercons_train_data_long[id == 1 & class == 1]$value, xlab = "Time",main = "Powercons")
```


```{r}
powercons_train_data = powercons_train_data[,2:(ncol(powercons_train_data)-1)]
```

## Piecewise Approximation Approach

```{r}
train_nrow=nrow(powercons_train_data)
test_nrow=nrow(powercons_test_data)
segment_length=5
powercons_train_data_long=powercons_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=powercons_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa5=rbindlist(paa_list)
head(seg_paa5)
segment_length=10
powercons_train_data_long=powercons_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=powercons_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa10=rbindlist(paa_list) 
head(seg_paa10)
segment_length=20
powercons_train_data_long=powercons_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=powercons_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa20=rbindlist(paa_list) 
head(seg_paa20)

```

```{r}
plot(x=powercons_train_data_long[id==1 & class==1]$time,y=powercons_train_data_long[id==1 & class==1]$seg_paa5)
```


 
## Tree Piecewise Representation


```{r}
for (i in 1:length(unique(powercons_train_data_long$id))){
fit <- rpart(value~time,data = powercons_train_data_long[id == i],control = rpart.control(maxdepth = 2))
powercons_train_data_long[id == i,tree_piecewise:=predict(fit,powercons_train_data_long[id == i])]
}
plot(x = powercons_train_data_long[id == 10 & class == 1]$time,y = powercons_train_data_long[id == 10 & class == 1]$tree_piecewise)
``` 
 
 
 
```{r}
powercons_train_data_raw = data.frame()
for(i in 1:length(unique(powercons_train_data_long$id))){
powercons_train_data_raw = rbind(powercons_train_data_raw,t(as.data.frame(powercons_train_data_long[id == i]$value)))
}
row.names(powercons_train_data_raw) <- NULL
head(powercons_train_data_raw,10)
```



```{r}
powercons_train_data_tree_piecewise = data.frame()
for(i in 1:length(unique(powercons_train_data_long$id))){
    powercons_train_data_tree_piecewise = rbind(powercons_train_data_tree_piecewise,t(as.data.frame(powercons_train_data_long[id == i]$tree_piecewise)))
}
row.names(powercons_train_data_tree_piecewise) <- NULL
head(powercons_train_data_tree_piecewise,10)
```




```{r}
powercons_train_data_paa5 = data.frame()
for(i in 1:length(unique(powercons_train_data_long$id))){
    powercons_train_data_paa5 = rbind(powercons_train_data_paa5,t(as.data.frame(seg_paa5)))
}
row.names(powercons_train_data_paa5) <- NULL
head(powercons_train_data_paa5)
```


```{r}
powercons_train_data_paa10 = data.frame()
for(i in 1:length(unique(powercons_train_data_long$id))){
    powercons_train_data_paa10 = rbind(powercons_train_data_paa10,t(as.data.frame(seg_paa10)))
}
row.names(powercons_train_data_paa10) <- NULL
head(powercons_train_data_paa10)
```



```{r}
powercons_train_data_paa20 = data.frame()
for(i in 1:length(unique(powercons_train_data_long$id))){
    powercons_train_data_paa20 = rbind(powercons_train_data_paa20,t(as.data.frame(seg_paa20)))
}
row.names(powercons_train_data_paa20) <- NULL
head(powercons_train_data_paa20)
```






## Dataset 2: PLANE


```{r}
plane_train_data <- fread("Plane_TRAIN.txt")
plane_test_data <- fread("Plane_TEST.txt")

setnames(plane_train_data,"V1","class")
plane_train_data=plane_train_data[order(class)]
plane_train_data[,class:=as.character(class)]
plane_train_data[,id:=1:.N]
plane_train_data_long=melt(plane_train_data,id.vars=c('id','class'))
plane_train_data_long[,time:=as.numeric(gsub("\\D", "", variable))-1]
plane_train_data_long=plane_train_data_long[,list(id,class,time,value)]
plane_train_data_long=plane_train_data_long[order(id,time)]
head(plane_train_data_long)
```


```{r}

plot(x = plane_train_data_long[id == 1 & class == 1]$time,y = plane_train_data_long[id == 1 & class == 1]$value, xlab = "Time",main = "Plane")
```



```{r}
plane_train_data = plane_train_data[,2:(ncol(plane_train_data)-1)]
```


## Piecewise Approximation Approach


```{r}
train_nrow=nrow(plane_train_data)
test_nrow=nrow(plane_test_data)
segment_length=5
plane_train_data_long=plane_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=plane_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa5=rbindlist(paa_list)
head(seg_paa5)
segment_length=10
plane_train_data_long=plane_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=plane_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa10=rbindlist(paa_list) 
head(seg_paa10)
segment_length=20
plane_train_data_long=plane_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=plane_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa20=rbindlist(paa_list) 
head(seg_paa20)

```


## Tree Piecewise Representation


```{r}
for (i in 1:length(unique(plane_train_data_long$id))){
fit <- rpart(value~time,data = plane_train_data_long[id == i],control = rpart.control(maxdepth = 2))
plane_train_data_long[id == i,tree_piecewise:=predict(fit,plane_train_data_long[id == i])]
}
plot(x = plane_train_data_long[id == 10 & class == 1]$time,y = plane_train_data_long[id == 10 & class == 1]$tree_piecewise)
``` 



```{r}
plane_train_data_raw = data.frame()
for(i in 1:length(unique(plane_train_data_long$id))){
plane_train_data_raw = rbind(plane_train_data_raw,t(as.data.frame(plane_train_data_long[id == i]$value)))
}
row.names(plane_train_data_raw) <- NULL
head(plane_train_data_raw,10)
```



```{r}
plane_train_data_tree_piecewise = data.frame()
for(i in 1:length(unique(plane_train_data_long$id))){
    plane_train_data_tree_piecewise = rbind(plane_train_data_tree_piecewise,t(as.data.frame(plane_train_data_long[id == i]$tree_piecewise)))
}
row.names(plane_train_data_tree_piecewise) <- NULL
head(plane_train_data_tree_piecewise)
```



```{r}
plane_train_data_paa5 = data.frame()
for(i in 1:length(unique(plane_train_data_long$id))){
    plane_train_data_paa5 = rbind(plane_train_data_paa5,t(as.data.frame(seg_paa5)))
}
row.names(plane_train_data_paa5) <- NULL
head(plane_train_data_paa5)
```



```{r}
plane_train_data_paa10 = data.frame()
for(i in 1:length(unique(plane_train_data_long$id))){
    plane_train_data_paa10 = rbind(plane_train_data_paa10,t(as.data.frame(seg_paa10)))
}
row.names(plane_train_data_paa10) <- NULL
head(plane_train_data_paa10)
```



```{r}
plane_train_data_paa20 = data.frame()
for(i in 1:length(unique(plane_train_data_long$id))){
    plane_train_data_paa20 = rbind(plane_train_data_paa20,t(as.data.frame(seg_paa20)))
}
row.names(plane_train_data_paa20) <- NULL
head(plane_train_data_paa20)
```


## Dataset 3: GunPointMaleVersusFemale


```{r}
gunpointMaleVersusFemale_train_data <- fread("GunPointMaleVersusFemale_TRAIN.txt")
gunpointMaleVersusFemale_test_data <- fread("GunPointMaleVersusFemale_TEST.txt")

setnames(gunpointMaleVersusFemale_train_data,"V1","class")
gunpointMaleVersusFemale_train_data=gunpointMaleVersusFemale_train_data[order(class)]
gunpointMaleVersusFemale_train_data[,class:=as.character(class)]
gunpointMaleVersusFemale_train_data[,id:=1:.N]
gunpointMaleVersusFemale_train_data_long=melt(gunpointMaleVersusFemale_train_data,id.vars=c('id','class'))
gunpointMaleVersusFemale_train_data_long[,time:=as.numeric(gsub("\\D", "", variable))-1]
gunpointMaleVersusFemale_train_data_long=gunpointMaleVersusFemale_train_data_long[,list(id,class,time,value)]
gunpointMaleVersusFemale_train_data_long=gunpointMaleVersusFemale_train_data_long[order(id,time)]
head(gunpointMaleVersusFemale_train_data_long)
```



```{r}
plot(x = gunpointMaleVersusFemale_train_data_long[id == 1 & class == 1]$time,y = gunpointMaleVersusFemale_train_data_long[id == 1 & class == 1]$value, xlab = "Time",main = "gunpointMaleVersusFemale")
```


```{r}
gunpointMaleVersusFemale_train_data = gunpointMaleVersusFemale_train_data[,2:(ncol(gunpointMaleVersusFemale_train_data)-1)]
```


## Piecewise Approximation Approach



```{r}
train_nrow=nrow(gunpointMaleVersusFemale_train_data)
test_nrow=nrow(gunpointMaleVersusFemale_test_data)
segment_length=5
gunpointMaleVersusFemale_train_data_long=gunpointMaleVersusFemale_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=gunpointMaleVersusFemale_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa5=rbindlist(paa_list)
head(seg_paa5)
segment_length=10
gunpointMaleVersusFemale_train_data_long=gunpointMaleVersusFemale_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=gunpointMaleVersusFemale_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa10=rbindlist(paa_list) 
head(seg_paa10)
segment_length=20
gunpointMaleVersusFemale_train_data_long=gunpointMaleVersusFemale_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=gunpointMaleVersusFemale_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa20=rbindlist(paa_list) 
head(seg_paa20)

```


## Tree Piecewise Representation


```{r}
for (i in 1:length(unique(gunpointMaleVersusFemale_train_data_long$id))){
fit <- rpart(value~time,data = gunpointMaleVersusFemale_train_data_long[id == i],control = rpart.control(maxdepth = 2))
gunpointMaleVersusFemale_train_data_long[id == i,tree_piecewise:=predict(fit,gunpointMaleVersusFemale_train_data_long[id == i])]
}
plot(x = gunpointMaleVersusFemale_train_data_long[id == 10 & class == 1]$time,y = gunpointMaleVersusFemale_train_data_long[id == 10 & class == 1]$tree_piecewise)
``` 



```{r}
gunpointMaleVersusFemale_train_data_raw = data.frame()
for(i in 1:length(unique(gunpointMaleVersusFemale_train_data_long$id))){
gunpointMaleVersusFemale_train_data_raw = rbind(gunpointMaleVersusFemale_train_data_raw,t(as.data.frame(gunpointMaleVersusFemale_train_data_long[id == i]$value)))
}
row.names(gunpointMaleVersusFemale_train_data_raw) <- NULL
head(gunpointMaleVersusFemale_train_data_raw,10)
```


```{r}
gunpointMaleVersusFemale_train_data_tree_piecewise = data.frame()
for(i in 1:length(unique(gunpointMaleVersusFemale_train_data_long$id))){
   gunpointMaleVersusFemale_train_data_tree_piecewise = rbind(gunpointMaleVersusFemale_train_data_tree_piecewise,t(as.data.frame(gunpointMaleVersusFemale_train_data_long[id == i]$tree_piecewise)))
}
row.names(gunpointMaleVersusFemale_train_data_tree_piecewise) <- NULL
head(gunpointMaleVersusFemale_train_data_tree_piecewise)
```



```{r}
gunpointMaleVersusFemale_train_data_paa5 = data.frame()
for(i in 1:length(unique(gunpointMaleVersusFemale_train_data_long$id))){
   gunpointMaleVersusFemale_train_data_paa5 = rbind(gunpointMaleVersusFemale_train_data_paa5,t(as.data.frame(seg_paa5)))
}
row.names(gunpointMaleVersusFemale_train_data_paa5) <- NULL
head(gunpointMaleVersusFemale_train_data_paa5)
```



```{r}
gunpointMaleVersusFemale_train_data_paa10 = data.frame()
for(i in 1:length(unique(gunpointMaleVersusFemale_train_data_long$id))){
    gunpointMaleVersusFemale_train_data_paa10 = rbind(gunpointMaleVersusFemale_train_data_paa10,t(as.data.frame(seg_paa10)))
}
row.names(gunpointMaleVersusFemale_train_data_paa10) <- NULL
head(gunpointMaleVersusFemale_train_data_paa10)
```



```{r}
gunpointMaleVersusFemale_train_data_paa20 = data.frame()
for(i in 1:length(unique(gunpointMaleVersusFemale_train_data_long$id))){
    gunpointMaleVersusFemale_train_data_paa20 = rbind(gunpointMaleVersusFemale_train_data_paa20,t(as.data.frame(seg_paa20)))
}
row.names(gunpointMaleVersusFemale_train_data_paa20) <- NULL
head(gunpointMaleVersusFemale_train_data_paa20)
```



## Dataset 4: TRACE


```{r}
trace_train_data <- fread("Trace_TRAIN.txt")
trace_test_data <- fread("Trace_TEST.txt")

setnames(trace_train_data,"V1","class")
trace_train_data=trace_train_data[order(class)]
trace_train_data[,class:=as.character(class)]
trace_train_data[,id:=1:.N]
trace_train_data_long=melt(trace_train_data,id.vars=c('id','class'))
trace_train_data_long[,time:=as.numeric(gsub("\\D", "", variable))-1]
trace_train_data_long=trace_train_data_long[,list(id,class,time,value)]
trace_train_data_long=trace_train_data_long[order(id,time)]
head(trace_train_data_long)
```


```{r}
plot(x = trace_train_data_long[id == 1 & class == 1]$time,y = trace_train_data_long[id == 1 & class == 1]$value, xlab = "Time",main = "Trace")
```


```{r}
trace_train_data = trace_train_data[,2:(ncol(trace_train_data)-1)]
```


## Piecewise Approximation Approach


```{r}
train_nrow=nrow(trace_train_data)
test_nrow=nrow(trace_test_data)
segment_length=5
trace_train_data_long=trace_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=trace_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa5=rbindlist(paa_list)
head(seg_paa5)
segment_length=10
trace_train_data_long=trace_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=trace_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa10=rbindlist(paa_list) 
head(seg_paa10)
segment_length=20
trace_train_data_long=trace_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=trace_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa20=rbindlist(paa_list) 
head(seg_paa20)

```


## Tree Piecewise Representation


```{r}
for (i in 1:length(unique(trace_train_data_long$id))){
fit <- rpart(value~time,data = trace_train_data_long[id == i],control = rpart.control(maxdepth = 2))
trace_train_data_long[id == i,tree_piecewise:=predict(fit,trace_train_data_long[id == i])]
}
plot(x = trace_train_data_long[id == 10 & class == 1]$time,y = trace_train_data_long[id == 10 & class == 1]$tree_piecewise)
``` 


```{r}
trace_train_data_raw = data.frame()
for(i in 1:length(unique(trace_train_data_long$id))){
trace_train_data_raw = rbind(trace_train_data_raw,t(as.data.frame(trace_train_data_long[id == i]$value)))
}
row.names(trace_train_data_raw) <- NULL
head(trace_train_data_raw)
```


```{r}
trace_train_data_tree_piecewise = data.frame()
for(i in 1:length(unique(trace_train_data_long$id))){
   trace_train_data_tree_piecewise = rbind(trace_train_data_tree_piecewise,t(as.data.frame(trace_train_data_long[id == i]$tree_piecewise)))
}
row.names(trace_train_data_tree_piecewise) <- NULL
head(trace_train_data_tree_piecewise)
```


```{r}
trace_train_data_paa5 = data.frame()
for(i in 1:length(unique(trace_train_data_long$id))){
   trace_train_data_paa5 = rbind(trace_train_data_paa5,t(as.data.frame(seg_paa5)))
}
row.names(trace_train_data_paa5) <- NULL
head(trace_train_data_paa5)
```



```{r}
trace_train_data_paa10 = data.frame()
for(i in 1:length(unique(trace_train_data_long$id))){
    trace_train_data_paa10 = rbind(trace_train_data_paa10,t(as.data.frame(seg_paa10)))
}
row.names(trace_train_data_paa10) <- NULL
head(trace_train_data_paa10)
```


```{r}
trace_train_data_paa20 = data.frame()
for(i in 1:length(unique(trace_train_data_long$id))){
   trace_train_data_paa20 = rbind(trace_train_data_paa20,t(as.data.frame(seg_paa20)))
}
row.names(trace_train_data_paa20) <- NULL
head(trace_train_data_paa20)
```



## Dataset 5: GunPointOldVersusYoung


```{r}
gunpointoldVersusyoung_train_data <- fread("GunPointOldVersusYoung_TRAIN.txt")
gunpointoldVersusyoung_test_data <- fread("GunPointOldVersusYoung_TEST.txt")

setnames(gunpointoldVersusyoung_train_data,"V1","class")
gunpointoldVersusyoung_train_data=gunpointoldVersusyoung_train_data[order(class)]
gunpointoldVersusyoung_train_data[,class:=as.character(class)]
gunpointoldVersusyoung_train_data[,id:=1:.N]
gunpointoldVersusyoung_train_data_long=melt(gunpointoldVersusyoung_train_data,id.vars=c('id','class'))
gunpointoldVersusyoung_train_data_long[,time:=as.numeric(gsub("\\D", "", variable))-1]
gunpointoldVersusyoung_train_data_long=gunpointoldVersusyoung_train_data_long[,list(id,class,time,value)]
gunpointoldVersusyoung_train_data_long=gunpointoldVersusyoung_train_data_long[order(id,time)]
head(gunpointoldVersusyoung_train_data_long)
```



```{r}
plot(x = gunpointoldVersusyoung_train_data_long[id == 1 & class == 1]$time,y = gunpointoldVersusyoung_train_data_long[id == 1 & class == 1]$value, xlab = "Time",main = "GunPointOldVersusYoung")
```


```{r}
gunpointoldVersusyoung_train_data = gunpointoldVersusyoung_train_data[,2:(ncol(gunpointoldVersusyoung_train_data)-1)]
```


## Piecewise Approximation Approach


```{r}
train_nrow=nrow(gunpointoldVersusyoung_train_data)
test_nrow=nrow(gunpointoldVersusyoung_test_data)
segment_length=5
gunpointoldVersusyoung_train_data_long=gunpointoldVersusyoung_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=gunpointoldVersusyoung_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa5=rbindlist(paa_list)
head(seg_paa5)
segment_length=10
gunpointoldVersusyoung_train_data_long=gunpointoldVersusyoung_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=gunpointoldVersusyoung_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa10=rbindlist(paa_list) 
head(seg_paa10)
segment_length=20
gunpointoldVersusyoung_train_data_long=gunpointoldVersusyoung_train_data_long[order(id,time)]
paa_result=vector('list',train_nrow)
for (i in 1:train_nrow){
      data_ts=gunpointoldVersusyoung_train_data_long[id==i]$value
      paa_repr=repr_paa(data_ts,segment_length,meanC)
      paa_result[[i]]=paa_repr 
}
paa_list=vector('list', train_nrow)
for (i in 1:train_nrow) {
      paa_list[[i]]=as.data.table(t(paa_result[[i]]))
}
seg_paa20=rbindlist(paa_list) 
head(seg_paa20)
```


## Tree Piecewise Representation


```{r}
for (i in 1:length(unique(gunpointoldVersusyoung_train_data_long$id))){
fit <- rpart(value~time,data = gunpointoldVersusyoung_train_data_long[id == i],control = rpart.control(maxdepth = 2))
gunpointoldVersusyoung_train_data_long[id == i,tree_piecewise:=predict(fit,gunpointoldVersusyoung_train_data_long[id == i])]
}
plot(x = gunpointoldVersusyoung_train_data_long[id == 10 & class == 1]$time,y = gunpointoldVersusyoung_train_data_long[id == 10 & class == 1]$tree_piecewise)
``` 



```{r}
gunpointoldVersusyoung_train_data_raw = data.frame()
for(i in 1:length(unique(gunpointoldVersusyoung_train_data_long$id))){
gunpointoldVersusyoung_train_data_raw = rbind(gunpointoldVersusyoung_train_data_raw,t(as.data.frame(gunpointoldVersusyoung_train_data_long[id == i]$value)))
}
row.names(gunpointoldVersusyoung_train_data_raw) <- NULL
head(gunpointoldVersusyoung_train_data_raw)
```



```{r}
gunpointoldVersusyoung_train_data_tree_piecewise = data.frame()
for(i in 1:length(unique(gunpointoldVersusyoung_train_data_long$id))){
   gunpointoldVersusyoung_train_data_tree_piecewise = rbind(gunpointoldVersusyoung_train_data_tree_piecewise,t(as.data.frame(gunpointoldVersusyoung_train_data_long[id == i]$tree_piecewise)))
}
row.names(gunpointoldVersusyoung_train_data_tree_piecewise) <- NULL
head(gunpointoldVersusyoung_train_data_tree_piecewise)
```



```{r}
gunpointoldVersusyoung_train_data_paa5 = data.frame()
for(i in 1:length(unique(gunpointoldVersusyoung_train_data_long$id))){
   gunpointoldVersusyoung_train_data_paa5 = rbind(gunpointoldVersusyoung_train_data_paa5,t(as.data.frame(seg_paa5)))
}
row.names(gunpointoldVersusyoung_train_data_paa5) <- NULL
head(gunpointoldVersusyoung_train_data_paa5)
```



```{r}
gunpointoldVersusyoung_train_data_paa10 = data.frame()
for(i in 1:length(unique(gunpointoldVersusyoung_train_data_long$id))){
    gunpointoldVersusyoung_train_data_paa10 = rbind(gunpointoldVersusyoung_train_data_paa10,t(as.data.frame(seg_paa10)))
}
row.names(gunpointoldVersusyoung_train_data_paa10) <- NULL
head(gunpointoldVersusyoung_train_data_paa10)
```



```{r}
gunpointoldVersusyoung_train_data_paa20 = data.frame()
for(i in 1:length(unique(gunpointoldVersusyoung_train_data_long$id))){
   gunpointoldVersusyoung_train_data_paa20 = rbind(gunpointoldVersusyoung_train_data_paa20,t(as.data.frame(seg_paa20)))
}
row.names(gunpointoldVersusyoung_train_data_paa20) <- NULL
head(gunpointoldVersusyoung_train_data_paa20)
```











